\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=3cm, right=3cm, top=2cm]{geometry}

\title{\textbf{Understanding Homeopathy with Artificial Intelligence}}
\author{Neelkant Newra \\ National Institute of Technology, Raipur \\ Email: newra008@gmail.com}
\date{August 2021}

\begin{document}
\maketitle
\section*{Summary}

Homeopathy is an alternative medical method that is based on pseudoscience. Samuel Hahnemann, a German physician, came up with the idea in 1796. Homeopaths believe that a substance that produces illness symptoms in healthy individuals may also cure comparable symptoms in sick people; this theory is known as \textbf{similia similibus curentur}, or \textbf{"like heals like."} Remedies are homoeopathic medicines that are prepared using homoeopathic dilution. The chosen ingredient is diluted repeatedly until the final result is chemically indistinguishable from the diluent in this process. In many cases, not even a single molecule of the original material will remain in the finished product.Homeopaths may strike and/or shake the product between dilutions, saying that this causes the diluent to recall the original ingredient after it is removed. Practitioners believe that ingesting such concoctions may heal or cure illness.\\


Since at least the mid-nineteenth century, all relevant scientific information concerning physics, chemistry, biochemistry, and biology has contradicted homoeopathy. Homeopathic medicines are biochemically inert and have no known side effects. The later discovery of viruses and bacteria as illness causes contradicts Hahnemann's theory of disease, which is based on concepts he calls miasms. Clinical experiments have been undertaken, and the results have shown that homoeopathic medicines have no objective impact. Homeopathy has been labelled "quackery" by scientific and medical organisations because of its basic implausibility and lack of demonstrated efficacy. \\


We all know that Homeopathy is a late curing treatment which works on the root as per suggested by the practitioner. There are lots of beneficiary who are setting example of its effectiveness almost after a long duration of time. So how artificial intelligence will help here?  Through AI we can keep a track of patient record and time of recovery, if we find similar type of recovery duration vs similar medicine then we can relate the correctness of the medicine. Apart from this we have to also consider the intermediate treatment taken during the validation period. \\

We can follow the list of approach to validate the Pseudoscience behind the Homeopathy:

\begin{itemize}
	\item Tracking the time record of Recovery duration.
	\item Intermediate alternative treatment during the validation Period.
	\item List of Patient who recover or not recover
\end{itemize}
\end{document}
